Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-14 CORL/example.tex
Improved texture reality subsection

		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
		Instead of feeding input scenes $s$ directly into the image translator $\Tab$, we first apply learnable textures $\tau$ to their surfaces as shown in figure \ref{fig:main_diagram}.
		Previous works called these learnable textures ``neural textures'', and were parametrized as a discrete grid of differentiable texels. 
		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
		In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are parametrized continuously over UV space using a neural network.
		Like previous works, our neural textures $\tau\toL$ are learned jointly with our image translator $T$.

@@

		% For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
		We define an image similarity loss between two image-like tensors that returns a score between 0 and 1, where 0 means perfect similarity:
		\begin{equation}
			\similar(x,y) = L_2(x,y)-\msssim(x,y) 
		\end{equation}
		This function combines mean pixel-wise $L_2$ distance (used in MUNIT) with multi-scale structural image similarity $\msssim$, introduced in \citep{msssim}.

@@

		To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...

@@

		To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output by introducing a ``texture realism'' loss $\lTR$. 
		$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
		\begin{equation}
			\lTR \Rightarrow \pi \approx \ph
		\end{equation}
		% As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.

		This loss forces the neural textures to look realistic, instead of allowing them to have arbitrary colors.
		In other words, $\lTR$ makes the neural textures more realistic by making their projections look more realistic, like the final outputs.

		% So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
		% If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
		% However, we can improve this further.

		% Up until now we have not put any constraints on this neural texture. 
		Without $\lTR$, $\tau$ can look wildly different each time you train it.
		As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic - the colors are completely arbitrary.
		After adding $\lTR$ though, $\pih \approx \ph$, and $\tau$ to represents the albedo of the surfaces in the scene.
		The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.

		We can achieve surface-consistent translations just using $\lUC$, without $\lTR$.
		The the reverse is also true: $\lTR$ is sufficient to ensure surface consistency without $\lUC$.
		Using both, however, yields better results than either loss alone. 
		% For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.

		There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
		Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch as you would with $\lUC$.

>>>>

		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
		Instead of feeding input scenes $s$ directly into the image translator $\Tab$, we first apply learnable textures $\tau$ to their surfaces as shown in figure \ref{fig:main_diagram}.
		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
		In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are parametrized continuously over UV space using a neural network.
		Like previous works, our neural textures $\tau\toL$ are learned jointly with our image translator $T$.

@@

		% For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
		We define an image similarity loss $\similar$ between two image-like tensors $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
		\begin{equation}
			\similar(x,y) = L_2(x,y)-\msssim(x,y) 
		\end{equation}
		This function combines mean pixel-wise $L_2$ distance (used in MUNIT) with multi-scale structural image similarity $\msssim$, introduced in \citep{msssim}.

@@

		% To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...

@@

		To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output by introducing a ``texture realism'' loss $\lTR$. 
		$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
		% As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
		% This loss forces the neural textures to look realistic, instead of allowing them to have arbitrary colors.
		% In other words, $\lTR$ makes the neural textures more realistic by making their projections look more realistic, like the final outputs.
		\begin{equation}
			\lTR = \similar(\pi,\ph)
		\end{equation}
		% So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
		% If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
		% However, we can improve this further.
		% Up until now we have not put any constraints on this neural texture. 
		Without $\lTR$, $\tau$ can look wildly different each time you train it.
		As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic – the colors are completely arbitrary.
		After adding $\lTR$ though, $\pih \approx \ph$, and $\tau$ to represents the albedo of the surfaces in the scene.
		% The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.

		As it turns out, we can achieve surface-consistent translations just using $\lTR$, without $\lUC$.
		The the reverse is also true: $\lTR$ is sufficient to ensure surface consistency without $\lUC$.
		Using both, however, yields better results than either loss alone. 
		% For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.

		With that said, there are some advantages to using $\lTR$ alone: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
		Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch as you would with $\lUC$.
